A systematic search for transiting planets using \KT

### 2015-02-12 ms.tex
editing photometry

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\jwst}{\project{JWST}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{ketu}}

@@

In this \paper\ we present a data-analysis technique for exoplanet search and
characterization that is insensitive to spacecraft-induced trends in the light
curves.
We assume that the trends in the observed light curves in each star due to
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of a
huge number of these basis vectors and a transit model.
Our method builds on the ideas of previous data-driven de-trending procedures
like Pre-search data conditioning \citep[PDC;][]{pdc1, pdc2} but we can use a
much more flexible systematics model without worrying about over-fitting.

@@

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involve some sort of pre-processing or ``de-trending'' step.
For example, \citet{Vanderburg:2014} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{Crossfield:2015} iteratively construct a robust Gaussian
Process model for the photometry as a function of the measured centroids and
de-trend using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To make use of this, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{pdc1, pdc2}.
Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
a basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.

@@

The key insight in our transit search method that sets it apart from the
other standard procedures is that no de-trending is necessary.
Instead, we can fit for the noise (or trends) and signal simultaneously.
This is theoretically appealing because it will be more sensitive to low
signal-to-noise transits.
The main reason for this is that the signal is not exactly orthogonal to the
systematics and the de-trending will over-fit causing the signal to be
distorted and weaker.
In order to reduce this effect, most procedures use a very rigid model for
the trends.
For \KT, this has been implemented by asserting that the centroids contain
all of the information needed to describe the trends.
In the \kepler\ pipeline, this is implemented by only allowing a small number
of PCA components to contribute to the fit.

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
out more flexible model should capture the systematic effects more robustly
but there is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.

>>>>

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\jwst}{\project{JWST}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\pdc}{\project{PDC}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{ketu}}

@@

In this \paper\ we present a data-analysis technique for exoplanet search and
characterization that is insensitive to spacecraft-induced trends in the light
curves.
We assume that the trends in the observed light curves in each star due to
spacecraft motion are shared by each star, and run PCA to measure the dominant
modes.
We then search for planets by modeling the data as a linear combination of a
huge number of these basis vectors and a transit model.
Our method builds on the ideas of previous data-driven de-trending procedures
like Pre-search data conditioning \citep[\pdc;][]{pdc1, pdc2} but we can use a
much more flexible systematics model without worrying about over-fitting.

@@

All previous methods for analyzing \KT\ data involve some sort of
``correction'' or ``de-trending'' step based on measurements of the pointing
motion of the spacecraft \citep{Vanderburg:2014, Aigrain:2015,
Crossfield:2015}.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for in the raw
photometric light curves.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To make use of this, the \pdc\ component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``co-trending basis vectors''.
This basis of trends was found by running Principal Component Analysis (PCA)
on a large set of light curves and extracting the top few ($\sim 4$)
components \citep{pdc1, pdc2}.
Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
a basis of representative trends but, unlike \pdc, we retain and use
a large number of these components.
For clarity, we will refer to our basis as a set of ``eigen light curves''
(ELCs) and the full set is made available online (SOMEURL).
\Fig{pca} shows the top ten ELCs for Campaign 1.

@@

The key insight in our transit search method that sets it apart from the
other standard procedures is that no de-trending is necessary.
Instead, we can fit for the noise (or trends) and signal simultaneously.
This is theoretically appealing because it will be more sensitive to low
signal-to-noise transits.
The main reason for this is that the signal is not exactly orthogonal to the
systematics and the de-trending will over-fit causing the signal to be
distorted and weaker.
In order to reduce this effect, most procedures use a very rigid model for
the trends.
For \KT, this has been implemented by asserting that the centroids contain
all of the information needed to describe the trends \citep{Vanderburg:2014,
Aigrain:2015, Crossfield:2015}.
In the \kepler\ pipeline, this is implemented by only allowing a small number
of PCA components to contribute to the fit in the \pdc\ procedure.

Physically, the motivation for our model---and the \pdc\ model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
out more flexible model should capture the systematic effects more robustly
but there is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.
